Article title

### 2017-06-28 paper-webserver.tex
ADD: new 4th para - not sure about it

>>>>

Spfy enables processing of thousands of genome sequences using multiple modules. By using task queue workers, enabled by the Python-based Redis Queue library, performance can scale to available infrastructure. As a bioinformatics tool, we also prioritized reliability by integrating the open-source Sentry platform for real-time exception tracking. The use of Docker-Compose for orchestrating containers ensures that the entire platform, webservers, databases, and task workers, can be easily replicated by other researchers. We present Spfy as a template for brining advance in web application development and deployment to online bioinformatics platforms.
